\documentclass[12pt]{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{CAS 741: Problem Statement\\Stock Prediction\\}

\author{Renjie Zhang  400055358}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2017-09-15 & Renjie Zhang & Create file\\

... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

What Problem I need to solve\\
Stock Prediction is a very important technology in final industry. It is very complex because it was affected by many factors.  One of the popular alghrism prediction method is to train the historical data using machin learning and try to find out the trend. \\

What althrims, skills and tools will be required\\
With the development of Big Data and Machine learning, it is possible to obtain an very accurate prediction result. I am going to implement the prediction using big data and machine learning. Spark will be the big data plantform and python will be the programming language. Some regression methematic methods will be involved  into the calculation.\\


What is the difficulty\\
To ensure the accurcy, a large scale of data is needed. In this case it is nessary to run the program on a distributed system which grouped by couple of computers. Spark is the perfect tool to work on distributed systems.\\

\wss{Please use a column width of 80 characters.}
\wss{Be sure to spell check your work.}

\end{document}